### 2017-01-04 robust-software.tex
Clarifying note about version control

>>>>

Note: one practice \emph{not} included in the list below is the use of version control.
We think this is essential to building software,
and indeed to doing reproducible scientific work of any kind
\cite{wilson2014,wilson2016}.
However,
our focus in this short guide is on the software that is built,
not on the process used to build it.
